%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\vspace{-1ex}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
   \cventry
    {} % Role
    {WeatherNavBot - AI Chat Bot} % Event
    {} % Location
    {} % Date(s)
    {
    \vspace{-5ex}
      \begin{cvitems} % Description(s)
      \vspace{1.5ex}
        \item { Developed an interactive conversational weather and navigation agent written in Python that utilized various methods and APIs to understand and respond to relevant user questions. }
        \item {Utilized Wit-API to train and develop an existing AI that was used to identify specific traits, entities and intents with the user question.}
         \item { Utilized Google's API for relevant location, map, time,weather and translation information.}
      \end{cvitems}
    }
  

%---------------------------------------------------------
 \cventry
    {} % Role
    {Preet - Ecommerce Website} % Event
    {} % Location
    {} % Date(s)
    {
    \vspace{-5ex}
      \begin{cvitems} % Description(s)
      \vspace{1ex}
        \item {Developed an e-commerce website via PHP/HTML which utilized JDBC for a database of product information, pictures, customer information and addresses.}
        \item{It simulates an online store where a user can search for and purchase items, create an account, reset a password via email, and see their order history.} 
        \item{An admin can monitor all purchases and users, create new items to sell, remove items from store, and reset the database to a preset default.}
       % \item {}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {} % Role
    {Multi-Threaded Web Scheduler (Implementation in C++ and Java)} % Event
    {} % Location
    {} % Date(s)
    {
    \vspace{-5ex}
      \begin{cvitems} % Description(s)
        \item { Used semaphores and thread condition variables to handle simultaneous requests. Utilized conditional variables and semaphores to prevent multiple threads from accessing critical segments.}
       % \item {}
      \end{cvitems}
    }
%---------------------------------------------------------
 
%---------------------------------------------------------
 
   \cventry
    {} % Role
    {React Portfolio Website} % Event
    {} % Location
    {} % Date(s)
    {
    \vspace{-4ex}
      \begin{cvitems} % Description(s)
        \item { Developed a fully reactive web application for phones and PC on React for personal information.}
        \item { Utilized Tailwind, MaterialUI, and tsparticles for UI/UX components }
        \item { Utilized Google API for live map and E-mail service }
       % \item {}
      \end{cvitems}
    }
     \vspace{-3ex}
%--------------------------------------------------------- 


\end{cventries}